Tracing the Stellar Halos of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using Hyper Suprime-Cam

### 2017-06-06 draft/paper1_v11.tex
Jenny's comment: 2

    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling 
    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
    but its median \mden{} profile is still useful to show the overall trend and to 
    compare with previous work}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}. 
    These median \mden{} profiles have moderate differences in the inner region. 
    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
    shows slightly higher \mden{} value but similar slope. 
    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
    uniform properties in the inner region. \jenny{if we introduce this jargon we need
    to define it at the 1-3 sentence level. Do we need it? we are not resolving cores, right?}
    At these masses, most of them should be ``slow-rotating'' 
    (e.g.\ \citealt{Cappellari13b})``core''--elliptical galaxies 
    (e.g.\ \citealt{Lauer07}) that have ``boxy'' inner isophotal shapes and similar 
    slopes of the inner surface brightness profiles (e.g.\ \citealt{Kormendy2009,
    Schombert2015}).

>>>>

    Fig~\ref{fig:avg_prof} shows the median \mden{} profiles\footnote{The median 
    profiles along with their uncertainties are derived using bootstrap resampling 
    method} of massive central galaxies at $0.3 < z < 0.5$ in three \mtot{} 
    bins\footnote{The sample is clearly not complete in the lowest \mtot{} bin, 
    but its median \mden{} profile is still useful to show the overall trend and to 
    compare with previous work}. 
    As shown in the left panel of Fig~\ref{fig:avg_prof}, we can comfortably trace
    the \mden{} profiles of these massive galaxies out to 100 kpc 
    \textbf{individually}. 
    These median \mden{} profiles have moderate differences in the inner region. 
    Within inner 10 kpc, the median \mden{} profile of more massive galaxies 
    shows slightly higher \mden{} value but similar slope. 
    These massive galaxies ($\ge 10^{11.4} M_{\odot}$) are known to have quite 
    uniform properties in the inner region. 
    At these high \mstar{}, these massive elliptical galaxies are known to have 
    quite uniform structural (e.g. \mden{} profile, isophotal shape, 
    \citealt{Lauer07, Kormendy2009, Schombert2015} and kinematic (e.g. 
    \citealt{Cappellari13b}) properties.
